---
title: "Making result"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Making result}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ussie)
```

This is going to be more of a restating/remixing of the [S3 vignette in vctrs](https://vctrs.r-lib.org/articles/s3-vector.html), rather than a how-to-use-something-in-this-package.
Essentially, it's a set of notes to myself as I figure out how best to present it.

First a couple of namespace directives:

```r
usethis::use_package("vctrs")
```

Then, copy and paste into `ussie-package.R`:

```r
#' Internal vctrs methods
#  TODO: ask why it's important that this be documented, i.e. why not
#  just `@import vctrs` in the `usethis namespace`?
#'
#' @import vctrs
#' @keywords internal
#' @name ussie-vctrs
NULL
```

We need to define some functions:

- `new_result()`: low-level constructor
- `uss_result()`: high-level constructor
- `format.ussie_result()`: formatter
- `vec_ptype_abbr.ussie_result()`, `vec_ptype_fill.ussie_result()`: format helpers


