---
title: "ussie"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ussie}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The **ussie** pckage is designed as a teaching example for a course, Building Tidy Tools.
In this course, a student will build this package.
For each file, they will start with templated functions; they will edit the file themselves, according to the particular exercise. 

When a student has a function working the way they want it to work, they will add an exampe in this vignette. What follows is Ian's attempt to go through the exercise.

```{r setup}
library(ussie)
library(dplyr)

conflicted::conflict_prefer("filter", "dplyr")
```

You can use the ussie package to work with data for league-play matches for European Football Leagues.
The data is provided by James Curley's [**engsoccerdata**](https://CRAN.R-project.org/package=engsoccerdata) package: the CRAN version has results through summer 2016; the [GitHub version](https://github.com/jalapic/engsoccerdata) has more-recent results. 

To find out which leagues are available, use `uss_countries()`:

```{r uss_countries}
uss_countries()
```

To get the data for a given league, use `uss_get_matches()` with the `country`:

```{r uss_get_matches}
uss_get_matches("england")
```

`uss_get_matches()` also accepts `...` arguments; these are passed to `dplyr::filter()`:

```{r uss_get_matches_filter}
uss_get_matches(
  "england", 
  season == 1990, 
  home == "Leeds United" | visitor == "Leeds United"
)
```

In a `matches` tibble, each row is a unique football match. 
To make calculations over the course of a team's season, it may be useful to provide an additional form: a `teams_matches` tibble. 
In this form, each row is a match from the perpsective of one of its teams. 
Thus, each match can be represented by two rows, one for each team.

We can get `teams_matches` tibble using `uss_make_teams_matches()`:

```{r uss_make_matches_teams}
england_1_1990 <-
  uss_get_matches("england", tier == 1, season == 1990) |>
  uss_make_teams_matches()

england_1_1990
```

If we look at a specific date:

```{r england_1990_09_29}
england_1_1990 |>
  filter(date == as.Date("1990-09-29"))
```
You can see that each match is represented twice: once for the home team and once for the visiting team.
