---
title: "ussie"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ussie}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The **ussie** pckage is designed as a teaching example for a course, Building Tidy Tools.
In this course, a student will build this package.
For each file, they will start with templated functions; they will edit the file themselves, according to the particular exercise. 

When a student has a function working the way they want it to work, they will add an exampe in this vignette. What follows is Ian's attempt to go through the exercise.

```{r setup}
library(ussie)
library(dplyr)

conflicted::conflict_prefer("filter", "dplyr")
```

You can use the ussie package to work with data for league-play matches for European Football Leagues.
The data is provided by James Curley's [**engsoccerdata**](https://CRAN.R-project.org/package=engsoccerdata) package: the CRAN version has results through summer 2016; the [GitHub version](https://github.com/jalapic/engsoccerdata) has more-recent results. 

## Get match results

To find out which leagues are available, use `uss_countries()`:

```{r uss_countries}
uss_countries()
```

To get the data for a given league, use `uss_get_matches()` with the `country`:

```{r uss_get_matches}
uss_get_matches("england")
```

`uss_get_matches()` also accepts `...` arguments; these are passed to `dplyr::filter()`:

```{r uss_get_matches_filter}
uss_get_matches(
  "england", 
  season == 1990, 
  home == "Leeds United" | visitor == "Leeds United"
)
```

## Get match results for teams

In a `matches` tibble, each row is a unique football match. 
To make calculations over the course of a team's season, it may be useful to provide an additional form: a `teams_matches` tibble. 
In this form, each row is a match from the perpsective of one of its teams. 
Thus, each match can be represented by two rows, one for each team.

We can get `teams_matches` tibble using `uss_make_teams_matches()`:

```{r uss_make_matches_teams}
england_1_1990 <-
  uss_get_matches("england", tier == 1, season == 1990) |>
  uss_make_teams_matches()

england_1_1990
```

If we look at a specific date:

```{r england_1990_09_29}
england_1_1990 |>
  filter(date == as.Date("1990-09-29"))
```
You can see that each match is represented twice: once for the home team and once for the visiting team.

## Get season results

We have another form: a `seasons` tibble.
These contain results accumulated over seasons.
We have a couple of functions, each takes a `teams_matches` data frame:

  - `uss_make_seasons_cumulative()`: returns cumulative results following every team's matches.
  - `uss_make_seasons_final()`: returns results at the end of each team's seasons.
  
For each of these functions, the columns returned are the same: `matches`, `wins`, `losses`, etc:
  
```{r uss_make_seasons_cumulative}
england_1_1990 |>
  uss_make_seasons_cumulative() |>
  arrange(team, date)
```

```{r uss_make_seasons_final}
england_1_1990 |>
  uss_make_seasons_final() |>
  arrange(desc(points))
```

You can call these functions has an optional argument to specify points-per-win.
This argument, `fn_points_per_win` is meant to be a function, when called with arguments `country` and `season`, returns the number of points for a win that season.
A default, `uss_points_per_win()`, is provided:

```{r uss_points_per_win}
uss_points_per_win("england", 1980)
```

Any function you provide must be vectorised over `country` and `season`:

```{r uss_points_per_win2}
uss_points_per_win(c("england", "england"), c(1980, 1981))
```

If you just want to specify a constant two or three points per season, you can provide an anonymous function.
If you are using R > 4.1.0, you can use the new syntax:

```{r uss_points_per_win3}
p <- \(...) 3 # use dots to allow unspecified arguments to pass

p("england", 1066)
```

## Plot results over seasons

Of the countries included in `uss_countries()`, only `"england"` has data for more than one `tier`, where we can see the effects of relegation and promotion. 
You can use `uss_plot_seasons_tiers()` to look at performance over seasons, using data returned from `uss_make_seasons_final()`:

```{r leeds_norwich}
leeds_norwich <- 
  uss_get_matches("england") |>
  uss_make_teams_matches() |>
  filter(team %in% c("Leeds United", "Norwich City")) |>
  uss_make_seasons_final() |>
  arrange(team, season)

leeds_norwich
```

The default is to show the `wins` on the y-axis:

```{r plot_wins}
uss_plot_seasons_tiers(leeds_norwich)
```

You can provide an argument, `aes_y`, where you can supply an expression just as you would for ggplot2:

```{r plot_wins_losses}
uss_plot_seasons_tiers(leeds_norwich, aes_y = wins - losses)
```

## Add results

```{r uss_result}
uss_get_matches("italy") |>
  uss_make_teams_matches() |>
  mutate(
    result = uss_result(goals_for, goals_against),
    .after = opponent
  )
```
