---
title: "ussie"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ussie}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The **ussie** pckage is designed as a teaching example for a course, Building Tidy Tools.
In this course, a student will build this package.
For each file, they will start with templated functions; they will edit the file themselves, according to the particular exercise. 

When a student has a function working the way they want it to work, they will add an exampe in this vignette. What follows is Ian's attempt to go through the exercise.

```{r setup}
library(ussie)
```

You can use the ussie package to work with data for league-play matches for European Football Leagues.
The data is provided by James Curley's [**engsoccerdata**](https://CRAN.R-project.org/package=engsoccerdata) package: the CRAN version has results through summer 2016; the [GitHub version](https://github.com/jalapic/engsoccerdata) has more-recent results. 

To find out which leagues are available, use `uss_countries()`:

```{r uss_countries}
uss_countries()
```

To get the data for a given league, use `uss_get_matches()` with the `country`:

```{r uss_get_matches}
uss_get_matches("england")
```

`uss_get_matches()` also accepts `...` arguments; these are passed to `dplyr::filter()`:

```{r uss_get_matches_filter}
uss_get_matches(
  "england", 
  season == 1990, 
  home == "Leeds United" | visitor == "Leeds United"
)
```

